---
title: '22'
author: "jj"
date: '2020 4 17 '
output: html_document
---
---
title: "Option Pricing With Monte-Carlo Simulation"
author: '-'
date: '2020 4 16 '
output: html_document
---

## Tips. Option pricing with Monte Carlo Simulation
  
Assume the risk-free rate is 2%. Compute the option premium for the 6-month call with the exercise of $55 using
Monte Carlo Simulation. Compare the option pre- mium in the simulation with the option value in Black-Scholes. 
Check whether the value in Simulation converges to the option value in Black-Scholes as the number of simulations increases.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(progress)
```

(1) Monte-Carlo Simulation

```{r}

inter = 100
z = rnorm(inter, mean = 0, sd = 1)
print(z)
s0 = 50
k = 55
t = 0.5
r = 0.02
v = 0.3

hist(z)
plot(density(Z))
 

# Compute a simulated Stock price, St
St = S0 * exp((r - 0.5*v^2)*t + v*sqrt(t)*Z)
St
St = S0 * exp((r - 0.5*v^2)*t + v*sqrt(t)*Z)
# Compute call option payoff at expiration, Ct
Ct = ifelse(St-K > 0, St-K, 0)
Ct
E_Ct = mean(Ct)
E_Ct

# Risk-Neutral Valueation > Discounting expected payoff of thet call option at risk-free rate
MC_C = exp(-r*t) * E_Ct
MC_C

```

(2) Black-Sholes Option Pricing.

```{r}
d1 = (log(S0/K) + (r + (v^2)*0.5)*t) / (v*sqrt(t))
d2 = d1 - v*sqrt(t)
BS_C = S0 * pnorm(d1) - K*exp(-r*T) * pnorm(d2)
MC_C; BS_C
```

(3) Check whether the value in Simulation Converges to the option value in Black-Scholes as the number of simulation increases.

```{r}
MC_call = function(S0, iter){
  Z = rnorm(iter, mean = 0, sd = 1)
  S0 = S0
  K = K
  t = 0.5
  r = 0.02
  v = 0.3
  St = S0 * exp((r - 0.5*v^2)*t + v*sqrt(t)*Z)
  Ct = ifelse(St-K > 0, St-K, 0)
  E_Ct = mean(Ct)
  C = exp(-r*t) * E_Ct
  return(C)
  
}

a = c()
iter = 1000
pb = progress_bar$new(total = iter)

for (i in seq(1,1000)){
  pb$tick()
  Sys.sleep(0.01)
  a[i] = MC_call(S0, i)
}

plot(a, type='o')
abline(h = BS_C, col = 'blue')
MC_C; BS_C

```
